\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-23 OaklandSubmission/ld.tex
another nit
added some high level security theorems etc.

     \inferrule*[lab={\footnotesize{T-Inp}}]
               {
               }
               {
                 \Gamma \vdash \kw{in}_{j} : \sigma^{m} \leadsto \kw{in}^{\sigma}_{j}
               }

@@

\begin{theorem}[Correctness]
  $\forall\:\Gamma, s, \widetilde{s}, \Gamma', \rho, \widetilde{\rho}, \widehat{\rho_{1}}, \widehat{\rho_{2}}$, if:

@@

\subsubsection*{Security theorem}

  %% \\
  %% \[
  %% \begin{array}{rrcl}
  %%   \ftext{Value} & v &::=& c \mid [\overline{c_{i}}]_{n}\\
  %%   \ftext{Observation} & O &::=& \cdot \mid c; O\\
  %% \end{array}
  %% \]

>>>>

     \inferrule*[lab={\footnotesize{T-Inp}}]
               {
               }
               {
                 \Gamma \vdash \kw{in}_{j} : \sigma^{m} \leadsto \kw{in}^{m}_{j}
               }

@@

\begin{theorem}[Correctness]\label{theorem:correctness}
  $\forall\:\Gamma, s, \widetilde{s}, \Gamma', \rho, \widetilde{\rho}, \widehat{\rho_{1}}, \widehat{\rho_{2}}$, if:

@@

\nc{Super high level security theorem}
\subsubsection*{Security theorem} The protocols we generate provide simulation-based security against a semi-honest adversary, in the framework of ~\cite{gmw,can00,can01}. At a very high level, in this framework, parties are modeled as non-uniform interactive turing machines (ITMs), with inputs provided by an environment $\env$. An adversary $\adv$, selects and ``corrupts'' one of the parties - however, $\adv$ still follows the protocol specification. $\adv$ interacts with the $\env$, which observes the view of the corrupted party. At the end of the interaction, $\env$ outputs a single bit. Two different interactions are defined: the {\em real world} and an {\em ideal world}. In the real interaction, the parties run the protocol $\prot$ in the presence of $\adv$ and $\env$. Let $\real_{\prot,\adv,\env}$ denote the binary distribution ensemble describing $\env$'s output in this interaction. In the ideal interaction, parties send their inputs to an additional entity, a trusted functionality machine $\F$ that carries the desired computation truthfully. Let $\simu$ (the simulator) denote the adversary in this idealized execution, and $\ideal_{\F,\simu,\env}$ the binary distribution ensemble describing $\env$'s output after interacting with adversary $\simu$ and ideal functionality $\F$. A protocol $\prot$ is said to {\em securely realize} a functionality $\F$ if for every adversary $\adv$ in the real interaction, there is an adversary $\simu$ in the ideal interaction, such that no environment $\env$, on any input, can tell the real interaction apart from the ideal interaction, except with negligible probability (in the security parameter $\secparam$). More precisely, if the two binary distribution ensembles above are computationally indistinguishable.
\nc{I'm not happy with the theorem statement.}
\begin{theorem}[Security]\label{theorem:security}
Let $\F$ be a functionality in our source language with outputs (or observations) $O_1$, that is compiled into a protocol $\prot$ in our target language with outputs $O_2$, then $\prot$ securely realizes $\F$.  
\end{theorem}
\nc{We should probably connect things to earlier? Theorem 1 and 2 have very different languages.}
\noindent {\em Proof.} From Theorem \ref{theorem:correctness}, we have that the observations in $\prot$ and $\F$ are the same (i.e. $O_2 = O_1$). Now, from the simulation security of our backend (\cite{aby}), the proof of the above theorem follows. \nc{I dont know how to say more.}
  %% \\
  %% \[
  %% \begin{array}{rrcl}
  %%   \ftext{Value} & v &::=& c \mid [\overline{c_{i}}]_{n}\\
  %%   \ftext{Observation} & O &::=& \cdot \mid c; O\\
  %% \end{array}
  %% \]

### 2017-10-23 OaklandSubmission/pipe.tex
added some high level security theorems etc.

\section{Pipelining}
\label{sec:pipe}
\nc{Started high level description. Can go deeper and correct notation as we proceed.}
We now describe our technique of ``pipelining'' that allows us to compile and execute large programs that would otherwise have not fit in memory (due to the large size of the circuit generated by ABY). We do this securely in a manner such that the underlying backend (such as ABY in this case) does not have to modified in anyway and hence our technique is also compatible with any backend. In more detail, let $P$ be a program in our source language that gets compiled to $P'$ in our target language. In many cases, the ABY circuit generated for $P'$ is very large and cannot fit in memory (in fact, there is an upper limit of $2^{32}$ for the circuit size in ABY and for many natural programs, this upper limit is easily crossed). Without pipelining, we would be unable to compile and execute such a program $P$. In order to overcome this size limit, we do the following: we split the program $P$ into a sequence of smaller programs $Q_1||Q_2||\cdots||Q_k$ (that will be appropriately defined). We compile and execute each $Q_i$ separately, feeding the outputs of one program as state information to the next program. Of course, we have to be careful how we do this so as to not compromise the security of the protocol. More details follow.

@@

Our compiler, given $P$, will first split $P$ into $P_1||P_2||\cdots||P_k$ with the guarantee that the ABY circuits generated for every $Q_i$ defined above is small enough to fit into memory. It will then compile and execute the $k$ programs $Q_1||Q_2||\cdots||Q_k$ sequentially (freeing up memory usage after every execution) to produce final output $z$ to both parties.

>>>>

\section{Pipelining}
\label{sec:pipe}

We now describe our technique of ``pipelining'' that allows us to compile and execute large programs that would otherwise have not fit in memory (due to the large size of the circuit generated by ABY). We do this securely in a manner such that the underlying backend (such as ABY in this case) does not have to modified in anyway and hence our technique is also compatible with any backend. In more detail, let $P$ be a program in our source language that gets compiled to $P'$ in our target language. In many cases, the ABY circuit generated for $P'$ is very large and cannot fit in memory (in fact, there is an upper limit of $2^{32}$ for the circuit size in ABY and for many natural programs, this upper limit is easily crossed). Without pipelining, we would be unable to compile and execute such a program $P$. In order to overcome this size limit, we do the following: we split the program $P$ into a sequence of smaller programs $Q_1||Q_2||\cdots||Q_k$ (that will be appropriately defined). We compile and execute each $Q_i$ separately, feeding the outputs of one program as state information to the next program. Of course, we have to be careful how we do this so as to not compromise the security of the protocol. More details follow.

@@

Given $P$, we will first split $P$ into $P_1||P_2||\cdots||P_k$ with the guarantee that the ABY circuits generated for every $Q_i$ defined above is small enough to fit into memory. We then compile and execute the $k$ programs $Q_1||Q_2||\cdots||Q_k$ sequentially (freeing up memory usage after every execution) to produce final output $z$ to both parties.

\begin{theorem}[Pipelining security]
Let $P$ be a program in our source language with output $z$, that is split into programs $Q_1||Q_2||\cdots ||Q_k$ (as defined in the pipelining algorithm above) and compiled into protocols $\prot_1||\prot_2\cdots ||\prot_k$ that outputs $r_1||r_2||\cdots||z$ (to Party A) and $o_1||o_2||\cdots||z$ (to Party B), then $\prot$ securely realizes $P$.  
\end{theorem}

\noindent {\em Proof.} From Theorem \ref{theorem:security}, it follows that $\prot_i$ securely realizes $Q_i$ for every $1\leq i\leq k$. Hence, we know that the only information learnt by Party A is $r_1||r_2||\cdots||r_{k-1}||z$ and by Party B is $o_1||o_2||\cdots||o_{k-1}||z$. From the way we defined $r_i$ and $o_i$ ($1\leq i\leq k-1$), to be secret shares of $s_i$, they are individually uniformly random (in $(\mathbb{Z},+)$ and hence perfectly simulatable. From this, the proof of the above theorem follows.
